Mans not hot, Man can never be hot

### 2018-01-16 article/ms.tex
comments

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{
Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. Norfolk et al.]{Brodie J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
Andrew R. Casey,$^{1,2}$
Ernie? Kemp? Karakas? Lattanzio? \newauthor
Schlaufman? others?
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}

@@

% What's a barium star (as observed)? What is the s-process

% What causes a barium star? (extrinsic/intrinsic?)

% AGB stars and the s-process.

% Comparisons to expectations of theoretical birth rate
% Binary fraction at different metallicities
% Mass differentials of binary stars
% Yields of AGB stars at different masses and metallicities.
